The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
changed plot_crs to a function

%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
%the flagging process using the waterfall plot. Left: The glitch
%apparent at middle right is the same one whose time series is shown in
%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
%effect of the glitch also propagates over the other bolometers,
%appearing as a horizontal stripe. Right: The same data displayed with
%the time point including the glitch flagged out and rescaled}
%{fig:Flaggin}{1.0}
%
\Figure{crs}{The distribution of glitch amplitudes flagged and removed
from the data.  The expected contribution to the noise from the
unremoved glitches below the detection threshold is
\TBD.}{fig:GlitchDistribution}{1.0}

>>>>

%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
%the flagging process using the waterfall plot. Left: The glitch
%apparent at middle right is the same one whose time series is shown in
%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
%effect of the glitch also propagates over the other bolometers,
%appearing as a horizontal stripe. Right: The same data displayed with
%the time point including the glitch flagged out and rescaled}
%{fig:Flaggin}{1.0}
%
\Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
data in the \lon=111 field.  Glitches below the detection threshold may
contribute to the overall noise signal.}{fig:GlitchDistribution}{1.0}
